### 2020-04-08 3_implementation.tex
Fix typos.

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models (MPI and MPI+X), PGAS and actor
models (Chapel, Charm++ and X10), task-based systems (OmpSs, OpenMP
4.0, PaRSEC, Realm, Regent, and StarPU) and systems for large scale
data analytics, machine learning and workflows (Dask, Spark, Swift/T,
and TensorFlow). Implementing Task Bench in such a wide range of
systems is possible because the separation between core API (in
Table~\ref{tab:api}) and system implmentation enables an overall
effort of $\mathcal{O}(m + n)$ (for $m$ benchmarks on $n$ systems)
rather than $\mathcal{O}(mn)$ as has been the case for all previous
benchmarks that we know of. We briefly describe the systems and
implementations below.

>>>>

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models (MPI and MPI+X), PGAS and actor
models (Chapel, Charm++ and X10), task-based systems (OmpSs, OpenMP
4.0, PaRSEC, Realm, Regent, and StarPU) and systems for large scale
data analytics, machine learning and workflows (Dask, Spark, Swift/T,
and TensorFlow). Implementing Task Bench in such a wide range of
systems is possible because the separation between core API (in
Table~\ref{tab:api}) and system implementation enables an overall
effort of $\mathcal{O}(m + n)$ (for $m$ benchmarks on $n$ systems)
rather than $\mathcal{O}(mn)$ as has been the case for all previous
benchmarks that we know of. We briefly describe the systems and
implementations below.
